



```{r read, fig.width = 8, fig.height=8, eval=T, include=F}

# dpi = 200
source("00_common.R")
knitr::opts_chunk$set(echo = F)

# r$dtAll <- cansim::get_cansim("13-10-0810-01") %>%  setDT() # By cause
# r$dtAll <- cansim::get_cansim("13-10-0768-01") %>%  setDT()  # By Age
dtBirths0 <- cansim::get_cansim("13-10-0428") %>%  setDT() # Live births and fetal deaths (stillbirths), by type of birth (single or multiple)


dtBirths0 %>% names;
dtBirths <- dtBirths0 [, c(22,21,2,23,24) ] 


dtBirths$GEO %>% unique()
dtBirths[, GEO := gsub(", place of residence of mother", "", GEO)]




dtBirths <- dtBirths [
  Date> ym("2010-01") &
    GEO != "Northwest Territories including Nunavut" &
    GEO != "Yukon" &
    `Type of birth (single or multiple)` == "Total, single and multiple births"] %>% setorder(-Date)



dtBirths$`Type of birth (single or multiple)` <- NULL
setnames (dtBirths, "Live births and fetal deaths (stillbirths)", "type")
dtBirths[, GEO := gsub(", place of residence of mother", "", GEO)]
# dtBirths[, GEO:=as.factor(GEO)]

dtBirths[, GEO:=fct_relevel(GEO, aGeo)]
# dtBirths[, GEO:=factor(GEO)]
dtBirths[, Date:=year(Date)]


dtBirths[1:2]


dt.wide <-   dtBirths %>% dcast (Date + GEO ~ type, value.var = "val_norm" )


# It should be in rates per thousand TOTAL 1000 BIRTHS (not a percentage and not per 1000 live births.


dt.wide [ , `Stillbirths per thousand Total births` := round (1000 *`Fetal deaths (stillbirths)` / `Total, births`,0)] %>% setorder(GEO, -Date)


```



# Births


<!-- ## Search criteria: {data-width=100} -->

<!-- <font size=-1> -->

<!-- \ Data Source: [Statistics Canada Table 13-10-0810-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1310081001).  -->
<!-- Live births and fetal deaths (stillbirths), by type of birth (single or multiple). <br>Updated: Annually -->


<!-- ```{r} -->

<!-- selectInput("birth.type", "Birth Type", dtBirths$GEO %>% unique(), dtBirths$GEO %>% unique() %>% .[c(1,5,7,10,11)], multiple = T   ) -->

<!-- ``` -->


<!-- </font> -->






## ROW 1........ {.tabset .tabset-fade data-width=1000}

<!-- ## ROW 1........ -->


 Data Source: [Statistics Canada Table 13-10-0810-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1310081001). 
Live births and fetal deaths (stillbirths), by type of birth (single or multiple). Updated: Annually


### Chart

```{r}
# 
# ```{r fig.width = 8, fig.height=8}
# 
# out.width = "400px"
# out.width="50%"
# fig.dim = c(8, 6)

g <-  dt.wide [GEO != "Unknown province or territory"] %>% 
  ggplot(aes(Date, `Stillbirths per thousand Total births`, fill=GEO)) + 
      theme(legend.position = "bottom")  +
  geom_col() + geom_point (aes(size=`Total, births`)) + 
  facet_wrap(. ~ GEO, scales = "fixed") +     
  # theme(legend.position = "bottom")  +
  labs (
    title = "Stillbirths (per thousand Total births). Source: Statistics Canada Table 13-10-0810-01", 
    x = NULL,  y=NULL
  )


# 
# tryCatch({
#   observe({
#     if (input$birth.total==T) {
#       scaleFactor <- max(dt0$value, na.rm=T) / max(dt0$dose1_rate, na.rm=T)
#       
#       g <- g+
#         geom_line(aes(x=Date, y=dose2_rate * max(value, na.rm=T) / 100), col="red") +
#         scale_y_continuous(name="value", sec.axis=sec_axis(~./ (max(dt0$value, na.rm=T) / 100), name="Full vaccination rate"))     +
#         theme(
#           axis.title.y.left=element_text(color="blue"),
#           axis.text.y.left=element_text(color="blue"),
#           axis.title.y.right=element_text(color="red"),
#           axis.text.y.right=element_text(color="red")
#         )
#     }
#   })
  # 
# })  

# g
# 
# ```
# 
# ### Interactive plot
# 
# ```{r}
g %>% ggplotly


```



### Grid

```{r}

dt.wide %>%  datatable.title()

```



<!-- ### Grid (Raw data) -->

<!-- ```{r} -->

<!-- dtBirths %>%  datatable.title("Statistics Canada Table 13-10-0428. Live births and fetal deaths (stillbirths), by type of birth (single or multiple). Updated: Annually") -->

<!-- ``` -->


<!-- <!-- ### Timeseries  --> -->


<!-- ```{r eval=FALSE, include=FALSE} -->

<!-- # dt.wide[`Stillbirths per thousand Total births` <1000 ]  -->

<!-- dt.wide3 <-   dt.wide [`Stillbirths per thousand Total births` <100 ]  %>% dcast (Date ~ GEO, value.var = "Stillbirths per thousand Total births") -->
<!-- dt.wide3  %>% setcolorder("Date") %>% as.xts.data.table %>% dygraph.title("stillbirths / live births (%)") -->

<!-- ```   -->


<!-- >  Data Source: [Statistics Canada Table 13-10-0810-01](https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1310081001)  -->






